### 2018-05-01 Docs/runtime_parameters/runtime_parameters.tex

\rowcolor{tableShade}
\verb= burner_threshold_cutoff = &  Mass fraction cutoff for burner\_threshold\_species  used in burner threshold & 1.d-10 \\
\verb= burner_threshold_species = &  Name of the species to be used in burner threshold & "" \\
\rowcolor{tableShade}
\verb= do_burning = &  turn on (.true.) or off (.false.) burning & .true. \\
\verb= do_subgrid_burning = &  break a zone into subzones, call the burner in each subzone and then average the result to the original cell & .false. \\
\rowcolor{tableShade}
\verb= reaction_sum_tol = &  mass fraction sum tolerance (if they don't sum to 1 within this tolerance, we abort) & 1.d-10 \\

@@

\verb= beta_type = &  what type of coefficient to use inside the velocity divergence constraint. \newline {\tt beta\_type} = 1 uses $\beta_0$; \newline {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); \newline {\tt beta\_type} = 3 uses 1 (small-scale combustion). & 1 \\

@@

\verb= do_smallscale = &  force $\rho_0 = (\rho h)_0 = 0$, {\tt evolve\_base\_state = F} and {\tt beta\_type} = 3 & .false. \\

>>>>

\rowcolor{tableShade}
\verb= burner_threshold_cutoff = &  Mass fraction cutoff for burner\_threshold\_species  used in burner threshold & 1.d-10 \\
\verb= burner_threshold_species = &  Name of the species to be used in burner threshold & "" \\
\rowcolor{tableShade}
\verb= burning_cutoff_density = &  Burning cutoff density (do not burn if density is below this threshold) Initialized to zero, runtime_init() in probin.f90 will check to see if burning_cutoff_density < 0 and if so will set burning_cutoff_density = base_cutoff_density & -1.0d0 \\
\verb= do_burning = &  turn on (.true.) or off (.false.) burning & .true. \\
\rowcolor{tableShade}
\verb= do_subgrid_burning = &  break a zone into subzones, call the burner in each subzone and then average the result to the original cell & .false. \\
\verb= reaction_sum_tol = &  mass fraction sum tolerance (if they don't sum to 1 within this tolerance, we abort) & 1.d-10 \\

@@

\verb= beta0_type = &  what type of coefficient to use inside the velocity divergence constraint. \newline {\tt beta0\_type} = 1 uses $\beta_0$; \newline {\tt beta0\_type} = 2 uses $\rho_0$ (anelastic); \newline {\tt beta0\_type} = 3 uses 1 (small-scale combustion). & 1 \\

@@

\verb= do_smallscale = &  force $\rho_0 = (\rho h)_0 = 0$, {\tt evolve\_base\_state = F} and {\tt beta0\_type} = 3 & .false. \\
